GMSE: an R package for generalised management strategy evaluation

### 2017-11-17 notebook/ms/SI1.Rmd
Add suggestion from @ninbrm to emphasise suggested parameter value settings

---
title: 'GMSE: an R package for generalised management strategy evaluation'
author: A. Bradley Duthie, Jeremy J. Cusack, Isabel L. Jones, Erlend B. Nilsen, Roc&#0237;o
  A. Pozo, O. Sarobidy Rakotonarivo, Bram Van Moorter, and Nils Bunnefeld
date: '`r Sys.Date()`'
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    reference_docx: docx_template.docx
header-includes:
- \usepackage{lineno}
- \linenumbers
linestretch: 1
bibliography: gmse.bib
subtitle: Supporting Information 1
biblio-style: apalike
link-citations: true
linkcolor: blue
---

@@

After each individual in `POPULATION` is assigned a fitness, a tournament is used to select individuals. Tournament selection is an especially flexible, non-parametric method that samples a subset of individuals from the total population and chooses the fittest of the subset for replacement [@Hamblin2013]. In GMSE, tournament selection proceeds by randomly sampling `ga_sampleK` individuals from the total `POPULATION` with replacement. The fitnesses of the subset of `ga_sampleK` individuals are compared, and the `ga_chooseK` individuals of highest fitness are retained (if `ga_sampleK` $\geq$ `ga_chooseK`, then all `ga_sampleK` are chosen, but this is not recommended). Tournaments selecting `ga_chooseK` individuals from random subsets of size `ga_sampleK` continue until a total of `ga_popsize` individuals are retained.

>>>>

---
title: 'GMSE: an R package for generalised management strategy evaluation'
author: A. Bradley Duthie, Jeremy J. Cusack, Isabel L. Jones, Erlend B. Nilsen, Roc&#0237;o
  A. Pozo, O. Sarobidy Rakotonarivo, Bram Van Moorter, and Nils Bunnefeld
date: '`r Sys.Date()`'
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    reference_docx: docx_template.docx
header-includes:
- \usepackage{lineno}
- \linenumbers
linestretch: 1
link-citations: yes
linkcolor: blue
bibliography: gmse.bib
subtitle: Supporting Information 1
biblio-style: apalike
---

@@

After each individual in `POPULATION` is assigned a fitness, a tournament is used to select individuals. Tournament selection is an especially flexible, non-parametric method that samples a subset of individuals from the total population and chooses the fittest of the subset for replacement [@Hamblin2013]. In GMSE, tournament selection proceeds by randomly sampling `ga_sampleK` individuals from the total `POPULATION` with replacement. The fitnesses of the subset of `ga_sampleK` individuals are compared, and the `ga_chooseK` individuals of highest fitness are retained (if `ga_sampleK` $\geq$ `ga_chooseK`, then all `ga_sampleK` are chosen, but this will prevent adaptive evolution and is therefore not recommended). Tournaments selecting `ga_chooseK` individuals from random subsets of size `ga_sampleK` continue until a total of `ga_popsize` individuals are retained.
